---
title: "Effective Reproduction Number for BC, using real and simulated data"
author: "Nicola Mulberry, Caroline Colijn, Jessica Stockdale"
date: "12/06/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
theme_set(ggsidekick::theme_sleek())
library(tidyr)
library(lubridate)
library(reshape2)
library(dplyr)
library(EpiEstim)
library(gridExtra)

```
# Data

Get case count data for BC - real data and simulated relaxation data, at 3 different strengths

```{r}
bcdata = read.csv("../bc_casecounts2204.csv", header=TRUE)                
bcdata$Date = dmy(bcdata$Date)
bcdata$I = c(bcdata$Cases[2] - bcdata$Cases[1],
                 diff(bcdata$Cases))
bcdata <- bcdata %>% dplyr::rename(dates = Date) %>% dplyr::select(dates, I)

simdata65 = read.csv("../Simulated_data/relax_sim_065.csv", header=TRUE)   
simdata65$Date <- as.Date(simdata65$Date)
simdata65 <- simdata65 %>% dplyr::rename(dates = Date) %>% dplyr::rename(I = Diffs) %>% dplyr::select(dates, I)

simdata9 = read.csv("../Simulated_data/relax_sim_09.csv", header=TRUE)   
simdata9$Date <- as.Date(simdata9$Date)
simdata9 <- simdata9 %>% dplyr::rename(dates = Date) %>% dplyr::rename(I = Diffs) %>% dplyr::select(dates, I)

simdata5 = read.csv("../Simulated_data/relax_sim_05.csv", header=TRUE)   
simdata5$Date <- as.Date(simdata5$Date)
simdata5 <- simdata5 %>% dplyr::rename(dates = Date) %>% dplyr::rename(I = Diffs) %>% dplyr::select(dates, I)


```


# Estimation


```{r}

res <- estimate_R(bcdata, method = "parametric_si", config = make_config(list(
                                                    mean_si = 5, std_si = 1)))

plot(res)


res65 <- estimate_R(simdata65, method = "parametric_si", config = make_config(list(
                                                    mean_si = 5, std_si = 1)))
plot(res65)

res9 <- estimate_R(simdata9, method = "parametric_si", config = make_config(list(
                                                    mean_si = 5, std_si = 1)))
plot(res9)

res5 <- estimate_R(simdata5, method = "parametric_si", config = make_config(list(
                                                    mean_si = 5, std_si = 1)))
plot(res5)

```

# Time Rt>/<1 at 95% level 

```{r}
as.Date(res$R$t_end[min(which(res$R$`Quantile.0.975(R)` < 1))], origin=min(res$dates))

time_after65 = min(which(res65$R$`Quantile.0.025(R)`< 1))
time_after9 = min(which(res9$R$`Quantile.0.025(R)`< 1))

as.Date(res65$R$t_end[min(which(res65$R$`Quantile.0.025(R)` > 1)[which(res65$R$`Quantile.0.025(R)` > 1) > time_after65])], origin=min(res65$dates))

as.Date(res9$R$t_end[min(which(res9$R$`Quantile.0.025(R)` > 1)[which(res9$R$`Quantile.0.025(R)` > 1) > time_after9])], origin=min(res9$dates))
```



```{r}
p1 <- ggplot(data=res$R, aes(x=t_end, y=`Mean(R)`)) +
  geom_hline(yintercept=1, linetype="dashed", 
                color = "grey", size=1)+ylim(c(-0.5,6.2)) +
  geom_line()+
  geom_ribbon(aes(ymin = `Quantile.0.025(R)`,
                  ymax = `Quantile.0.975(R)`), fill = "#7ec5a3",alpha=0.4) +
  labs(x='Time (days)', y="Mean Rt") +
  geom_vline(xintercept = res$R$t_end[min(which(res$R$`Quantile.0.975(R)` < 1))],
             color = "#7ec5a3", size=1.5, alpha = 0.7) +
  annotate(geom = "text", x = res$R$t_end[min(which(res$R$`Quantile.0.975(R)` < 1))] - 1,
           y = 3, label = "Rt < 1", color = "black", angle = 90) +
  geom_vline(xintercept = 18, color = "gray25", size=1.5,
             alpha = 0.5) +
  annotate(geom = "text", x = 16.75, y = 1.7,
           label = "Physical distancing", color = "black", angle = 90)

p2 <- ggplot(data=res65$R, aes(x=t_end, y=`Mean(R)`)) +
  geom_hline(yintercept=1, linetype="dashed", 
                color = "grey", size=1)+ylim(c(0,7)) +
  geom_ribbon(aes(ymin = `Quantile.0.025(R)`,
                  ymax = `Quantile.0.975(R)`, fill = "#f7bb82"),alpha=0.4) +
  geom_ribbon(data = res9$R, aes(ymin = `Quantile.0.025(R)`,
                  ymax = `Quantile.0.975(R)`, fill = "#9caee4"),alpha=0.4) +
 # geom_ribbon(data = res5$R, aes(ymin = `Quantile.0.025(R)`,
 #                 ymax = `Quantile.0.975(R)`), fill = "#7ec5a3",alpha=0.4) +
  geom_line()+
  geom_line(data = res9$R, aes(x=t_end, y=`Mean(R)`)) +
 # geom_line(data = res5$R, aes(x=t_end, y=`Mean(R)`)) +
  labs(x='Time (days)', y="Mean Rt") +ylim(0, 3.5) +
  geom_vline(xintercept = res65$R$t_end[min(which(res65$R$`Quantile.0.025(R)` > 1)[which(res65$R$`Quantile.0.025(R)` > 1) > time_after65])],
             color = "#f7bb82", size=1.5, alpha = 0.7) +
  geom_vline(xintercept = res9$R$t_end[min(which(res9$R$`Quantile.0.025(R)` > 1)[which(res9$R$`Quantile.0.025(R)` > 1) > time_after9])],
             color = "#9caee4", size=1.5, alpha = 0.7) +
  annotate(geom = "text", x = res9$R$t_end[min(which(res9$R$`Quantile.0.025(R)` > 1)[which(res9$R$`Quantile.0.025(R)` > 1) > time_after9])] - 1.25, y = 3,
           label = "Rt > 1", color = "black", angle = 90) +
  annotate(geom = "text", x = res65$R$t_end[min(which(res65$R$`Quantile.0.025(R)` > 1)[which(res65$R$`Quantile.0.025(R)` > 1) > time_after9])] - 1.25, y = 3,
           label = "Rt > 1", color = "black", angle = 90) +
  geom_vline(xintercept = 17, color = "gray25", size=1.5,
             alpha = 0.5) +
  annotate(geom = "text", x = 15.75, y = 2.5,
           label = "Distancing relaxed", color = "black", angle = 90) +
  scale_fill_manual(name = expression(~f[2]), 
         values =c("#f7bb82"="#f7bb82","#9caee4"="#9caee4"), labels = c('0.9','0.65')) + theme(legend.position = c(0.93, 0.86),       legend.title=element_text(size=12), 
    legend.text=element_text(size=11))


grid.arrange(grobs = list(p1, p2), nrow = 2, heights = c(1,1))
```





## Timing
```{r}
test_Rt <- function(window, res){
    R_sample <- sample_posterior_R(res, n = 100, window = window)
    return(quantile(R_sample, probs=0.95))
}

win <- as.list(seq(1, nrow(res$R)))
test <- lapply(win, test_Rt, res=res)

# First < 1

first_div <- min(which(test <= 1))
first_div_date <- as.Date(res$R$t_end[first_div], origin=min(res$dates))
first_div_date

```
